
```{r setup, include=FALSE}
library(deSolve)
library(dplyr)
library(rstan)
library(outbreaks)
library(bayesplot)
#library(rstanarm)

rstan_options(auto_write = TRUE)           
options(mc.cores = parallel::detectCores())

knitr::opts_chunk$set(cache = TRUE, echo = TRUE, message = FALSE, warning = FALSE)
```



```{r load_flu_data, echo = TRUE}
#onset <- influenza_england_1978_school$date    
#cases <- influenza_england_1978_school$in_bed  #Number of students in bed
file='UK-HIV-AIDS.csv'
dataHIV = read.csv(file,header=FALSE)

hiv_data =dataHIV$V2
aids_data=dataHIV$V3

N = length(hiv_data) # Number of days observed throughout the outbreak
#n = as.integer(N*10 + 1)
pop = 66440000         # Population 
sample_time=0:(N-1)
sample_small_time=seq(from = 0, to =(N-1), length.out = 10*N+1 )
n = length(sample_small_time)


pred_days=N+1
times_pred = seq(0, pred_days, by = 1)
times_pred_small =seq(from = 0, to =pred_days, length.out = (pred_days+1)*10 +1 )
n_pred_sm = length(times_pred_small)
n_pred=length(times_pred)


sample_y <- cbind(hiv_data,aids_data);

# Modify data into a form suitable for Stan
flu_data = list(n_obs = N,
                n_small=n,
                n_small_pred=n_pred_sm,
                n_theta = 8,
                n_difeq = 3,
                n_pop = pop, #population
                y = sample_y, 
                t0 = -0.0000001,
#                t0 = 0.0,
                n_fake    = n_pred,
                fake_ts   = times_pred_small,
                tsm = sample_small_time,
                ts = sample_time)

# Specify parameters to monitor

parameters = c("y_init", "theta", "fake","R_0")  #deterministic models (Model 1, Model 2)
```

In the context of a deterministic SIR, in order to estimate the transmission and the recovery rate, we use two different specifications and we fit the models using Stan's NUTS algorithm and the mean-field ADVI variant.

## Model 1 - Poisson model

Stan model statement:

```{r stan_model1, echo=TRUE}
mod1_stat <- '
functions {
  real[] SIR(real t,  // time
  real[] y,           // system state {susceptible,infected,recovered}
  real[] theta,       // parameters
  real[] x_r,
  int[] x_i) {
  
  real mu= 0.0115;
  real nu= 0.0073;
  real kappa  =  0.00003;
  
  real beta   = theta[1];
  real sigma  = theta[2];
  real Karga1 = theta[3];
  real Karga2 = theta[4];
  real xi1    = theta[5];
  real xi2    = theta[6];  
  
  
  real dy_dt[3];
  
  dy_dt[1] =  mu -(beta*y[2] + nu + xi1  )*y[1];
  dy_dt[2]  =(beta* y[2] + xi1 ) *y[1] - (sigma + nu  - xi2)*y[2];
  dy_dt[3] = (sigma -xi2)* y[2] - (kappa + nu)*y[3];
  
  return dy_dt;
  }
  
  }
  data {
  
  int<lower = 1> n_obs;       // number of days observed
  int<lower = 1> n_small;       // number of days observed
  int<lower = 1> n_small_pred;       // number of days observed
  int<lower = 1> n_theta;     // number of model parameters
  int<lower = 1> n_difeq;     // number of differential equations
  int<lower = 1> n_pop;       // population 
  int y[n_obs,(n_difeq-1)];           // data, total number of infected individuals each day
  real t0;                // initial time point (zero)
  real ts[n_obs];         // time points observed
  real tsm[n_small];         // time points observed
  int<lower = 1> n_fake; // This is to generate "predicted"/"unsampled" data
  real fake_ts[n_small_pred]; // Time points for "predicted"/"unsampled" data
  
  }
  
  transformed data {
  real x_r[0];
  int x_i[0];
  }
  
  parameters {
  
  real<lower =  0, upper = 2.5> beta ;
  real<lower =  0, upper = 3.0> sigma ;
  real<lower =  0, upper = 1.> Karga1 ;
  real<lower =  0, upper = 1.> Karga2 ;
  real<lower =  0, upper = 1e-2> xi1 ;
  real<lower =  0, upper = 1> xi2 ;
  real<lower =  0, upper = 1e-4> I0 ;
  real<lower =  0, upper = 1e-4> A0 ;
 
  }
  
  transformed parameters{
  
  real y_hat[n_obs,(n_difeq-1)]; // solution from the ODE solver
  real y_hat_sm[n_small, n_difeq]; // solution from the ODE solver
  real y_init[n_difeq];     // initial conditions for both fractions of S and I
  real theta[n_theta];   // { alpha, beta, gamma, delta }
  

  real lambda1[n_obs];
  real lambda2[n_obs];
  real rho1[n_obs]; 
  real rho2[n_obs];
  vector[11] weights;
  vector[11] incidence1;
  vector[11] incidence2;
  real dt=1./(10*n_obs);


  

  y_init[1] = 1-(I0 + A0);
  y_init[2] = I0;
  y_init[3] = A0;
  
  
  theta[1] = beta;
  theta[2] = sigma;
  theta[3] = Karga1;
  theta[4] = Karga2;
  theta[5] = xi1;
  theta[6] = xi2;
  theta[7] = I0;
  theta[8] = A0;

  
  y_hat_sm = integrate_ode_rk45(SIR, y_init, t0, tsm, theta, x_r, x_i);

  
 weights[1]=0.5;
 weights[11]=0.5;
 
 for (i in 2:10){
     weights[i] = 1.0;
  }

 
  for (i in 1:n_obs){
      lambda1[i] = 0.0;
      lambda2[i] = 0.0;
      for (k in 1:11){
       incidence1[k] = (beta*y_hat_sm[k + 10*(i-1),2] + xi1 )*y_hat_sm[k + 10*(i-1),1];
       incidence2[k] = ( sigma- xi2 )*y_hat_sm[k + 10*(i-1),2];
       lambda1[i]    = lambda1[i] + dt*weights[k]*incidence1[k];
       lambda2[i]    = lambda2[i] + dt*weights[k]*incidence2[k];
      }
  y_hat[i,1]=n_pop*Karga1*lambda1[i];
  y_hat[i,2]=n_pop*Karga2*lambda2[i];
 }
    


  }
  
  
  model {
  
  real lamb1[n_obs];      //poisson parameter
  real lamb2[n_obs];      //poisson parameter
  real rhho1[n_obs];      //poisson parameter
  real rhho2[n_obs];      //poisson parameter
   
  vector[11] weight;
  vector[11] incid1;
  vector[11] incid2;
  real dtt=1./(10*n_obs);

  
  weight[1]=0.5;
  weight[11]=0.5;


  for (i in 2:10){
     weight[i] = 1.0;
  }
  
  //priors
  beta     ~ lognormal(0, 2.5);
  sigma    ~ uniform(0.0, 3. );
  Karga1   ~ uniform(0.0, 1. );
  Karga2   ~ uniform(0.0, 1.);
  xi1      ~ uniform(0.0, 1e-2 );
  xi2      ~ uniform(0.0, 1);
  I0       ~ uniform(0.0, 1e-4 );
  A0       ~ uniform(0.0, 1e-4 );  

  
  
  //likelihood
  for (i in 1:(n_obs)){
      lamb1[i] = 0.0;
      lamb2[i] = 0.0;
      for (k in 1:11){
       incid1[k] = ( beta*y_hat_sm[k + 10*(i-1),2] + xi1 )*y_hat_sm[k + 10*(i-1),1];
       incid2[k] = ( sigma- xi2 )*y_hat_sm[k + 10*(i-1),2];       
       lamb1[i]    = lamb1[i] +  dtt*weight[k]*incid1[k];
       lamb2[i]    = lamb2[i] +  dtt*weight[k]*incid2[k];       
      }
 
  rhho1[i] = n_pop*Karga1*lamb1[i];
  rhho2[i] = n_pop*Karga2*lamb2[i]; 
  y[i , 1] ~ poisson(rhho1[i]);;
  y[i , 2] ~ poisson(rhho2[i]);;
  }
 
  }
  
  generated quantities {
  real R_0;      // Basic reproduction number
  real nu= 0.0073;
  real epsilon = 1e-9;
  real fake[n_fake, 2];
  real <lower = 0.> y_hat_pred[n_small_pred, n_difeq]; // Output from the ODE solver
  
  real lamb1[n_fake];      //poisson parameter
  real lamb2[n_fake];      //poisson parameter
  real rhho1[n_fake];      //poisson parameter
  real rhho2[n_fake];      //poisson parameter
   
  vector[11] weight;
  vector[11] incid1;
  vector[11] incid2;
  real dtt  =1./(10*n_fake);

  
  weight[1]=0.5;
  weight[11]=0.5;


  for (i in 2:10){
     weight[i] = 1.0;
  }
  
  y_hat_pred = integrate_ode_rk45(SIR, y_init, t0, fake_ts, theta, x_r, x_i);  
  
    //likelihood
  for (i in 1:(n_fake)){
      lamb1[i] = 0.0;
      lamb2[i] = 0.0;
      for (k in 1:11){
       incid1[k] = ( theta[1]*y_hat_pred[k + 10*(i-1),2] + xi1 )*y_hat_pred[k + 10*(i-1),1];
       incid2[k] = ( theta[2]- xi2 )*y_hat_pred[k + 10*(i-1),2];       
       lamb1[i]   = lamb1[i] +  dtt*weight[k]*incid1[k];
       lamb2[i]   = lamb2[i] +  dtt*weight[k]*incid2[k];       
      }
 
  rhho1[i]=n_pop*theta[3]*lamb1[i];
  rhho2[i]=n_pop*theta[4]*lamb2[i];
  fake[i , 1] = poisson_rng( rhho1[i] );
  fake[i , 2] = poisson_rng( rhho2[i] );
 
  }
  
  R_0 = theta[1]/(theta[2] + nu);
  }
'

m1 <- stan_model(model_code = mod1_stat)
```

Fit and sample from the posterior using Hamiltonian Monte Carlo-NUTS:

```{r NUTS_fit1, dependson=c(load_flu_data) , echo=FALSE}
n_chains=6
n_warmups=5000
n_iter=10000
n_thin=1
set.seed(1234)
# Set initial values:     

ini_1 = function(){
   list(theta=c(runif(1,0,2.5), runif(1,0,3.), runif(1,0,1), runif(1,0,1),
                runif(1,0,1e-2), runif(1,0,1), 
                runif(1,0,1e-4), runif(1,0,1e-4)
                )  )   
  }

time.start_nuts1 <- Sys.time()
nuts_fit_1 = sampling(m1, data = flu_data, pars = parameters, init = ini_1, chains = n_chains, algorithm = 'NUTS',warmup = n_warmups, iter = n_iter, thin=n_thin, seed=13219)
time.end_nuts1 <- Sys.time()
duration_nuts1<- time.end_nuts1 - time.start_nuts1
  
nuts_fit_1_summary <- summary(nuts_fit_1, pars = c("lp__", "theta[1]", "theta[2]",
                                               "theta[3]", "theta[4]","theta[5]", "theta[6]","y_init")  )$summary
print(nuts_fit_1_summary,scientific=TRUE,digits=4)
posts_1 <-  rstan::extract(nuts_fit_1)
```


Check HMC diagnostics:

```{r diagnostics1, echo=FALSE}
mod1_diagnostics <-rstan::get_sampler_params(nuts_fit_1)

# Check for divergent transitions
rstan::check_divergences(nuts_fit_1)

posterior_1 <- as.array(nuts_fit_1)
color_scheme_set("viridis")
# Markov chain traceplots
mcmc_trace(posterior_1, pars="lp__")
mcmc_trace(posterior_1, pars=c("theta[1]", "theta[2]","theta[3]",
                               "theta[4]","theta[5]", "theta[6]",
                               "y_init[2]", "y_init[3]") )


# Univariate and bivariate marginal posterior distributions
pairs(nuts_fit_1, pars = c("theta[1]", "theta[2]","theta[3]",
                               "theta[4]","theta[5]", "theta[6]",
                               "y_init[2]", "y_init[3]"), 
      labels    = c("beta", "sigma","K1","K2","xi1","xi2","I0","A0"), 
      cex.labels=1.5, font.labels=9, condition = "accept_stat__")  



# Kernel density estimates of each Markov chain separately, overlaid
mcmc_dens_overlay(posterior_1, pars=c("theta[1]", "theta[2]","theta[3]",
                               "theta[4]","theta[5]", "theta[6]",
                               "y_init[2]", "y_init[3]") )

#Central posterior uncertainty intervals
mcmc_intervals(posterior_1,pars = c("theta[1]"),prob_outer = 0.95)
mcmc_intervals(posterior_1,pars = c("theta[2]"),prob_outer = 0.95)
mcmc_intervals(posterior_1,pars = c("theta[3]"),prob_outer = 0.95)
mcmc_intervals(posterior_1,pars = c("theta[4]"),prob_outer = 0.95)
```



```{r plot_nuts_fit1, echo=FALSE}
HIV_people   =data.frame(hiv_data)
AIDS_people  =data.frame(aids_data)
```



```{r plot_advi_1, echo=FALSE}
# Model fitted values across the observed time period
#library(gridExtra)
fit_I <- posts_1$fake[,,1]
fit_SIR_I <- fit_I
median_I = apply(fit_SIR_I, 2, median)
low_I = apply(fit_SIR_I, 2, quantile, probs=c(0.025))
high_I = apply(fit_SIR_I, 2, quantile, probs=c(0.975))
df_fit_I = data.frame(median_I, low_I, high_I, times_pred)

fit_A <- posts_1$fake[,,2]
fit_SIR_A <- fit_A
median_A = apply(fit_SIR_A, 2, median)
low_A = apply(fit_SIR_A, 2, quantile, probs=c(0.025))
high_A = apply(fit_SIR_A, 2, quantile, probs=c(0.975))
df_fit_A = data.frame(median_A, low_A, high_A, times_pred)
#save(df_fit_I_vb_1,file="df_I_det_Poiss_vb.Rda")

#df_sample_N = data.frame(hiv_data, sample_time)  

ggplot() +
  geom_ribbon(aes(x=times_pred, ymin = low_I, ymax = high_I), fill = "orange", alpha = 0.6) +
  geom_point(data = HIV_people, aes(x=sample_time, y=hiv_data) ,shape = 19, size = 1.5) +
  geom_line(data = df_fit_I, aes(x=times_pred, y=median_I, color = "Median"), size = 1.1) +
  scale_colour_manual(name='', values=c('Data'='black', 'Median'='darkorange3'))+
#  guides(colour = guide_legend(override.aes = list(shape=c(16,NA), linetype=c(0,1))))+
#  theme_bw()+theme(text = element_text(size=20))+
  
  geom_ribbon(aes(x=times_pred, ymin = low_A, ymax = high_A), fill = "orange", alpha = 0.6) +
  geom_point(data = AIDS_people, aes(x=sample_time, y=aids_data) ,shape = 19, size = 1.5) +
  geom_line(data = df_fit_A, aes(x=times_pred, y=median_A, color = "Median"), size = 1.1) +
  scale_colour_manual(name='', values=c('Data'='black', 'Median'='darkorange3'))+
#  guides(colour = guide_legend(override.aes = list(shape=c(16,NA), linetype=c(0,1))))+
  labs(x = "Time (days)", y = "HIV-AIDS cases ") + 
  scale_x_continuous(limits=c(0, 30)) +
  scale_y_continuous(limits=c(0,8000)) +
  theme_bw()+theme(text = element_text(size=20))
  
 
```
















Approximate the posterior using ADVI(mean-field):

```{r ADVI_1, dependson=c(load_flu_data), echo=FALSE}
set.seed(1234)
# Set initial values:

ini_vb_1 = function(){
   list(theta=c(runif(1,0,1), runif(1,0,1), runif(1,0,30), runif(1,0,30),
                runif(1,0,1e-2), runif(1,0,1e-3), 
                runif(1,0,8e-5), runif(1,0,8e-5)
                )  )   
  }

#init = ini_vb_1
time.start_vb_1 <- Sys.time()
vb_fit_1=vb(m1, data = flu_data, pars = parameters , iter = 50000,algorithm="meanfield", tol_rel_obj = 0.001, seed=16735673)
time.end_vb_1 <- Sys.time()
vb_duration_1 <- time.end_vb_1 - time.start_vb_1

vb_fit_1_summary <- summary(vb_fit_1, pars = c("lp__", "theta[1]", "theta[2]",
                                               "theta[3]", "theta[4]","theta[5]", "theta[6]","y_init") )$summary
print(vb_fit_1_summary,scientific=FALSE,digits=4)
posts_vb_1 <-  rstan::extract(vb_fit_1)
```

Plot model fit, median and 95% credible interval:


```{r plot_nuts_fit1, echo=FALSE}
HIV_people   =data.frame(hiv_data)
AIDS_people  =data.frame(aids_data)
```




```{r plot_advi_1, echo=FALSE}
# Model fitted values across the observed time period
#library(gridExtra)
fit_I <- posts_vb_1$fake[,,1]
fit_SIR_vb_I <- fit_I
median_I = apply(fit_SIR_vb_I, 2, median)
low_I = apply(fit_SIR_vb_I, 2, quantile, probs=c(0.025))
high_I = apply(fit_SIR_vb_I, 2, quantile, probs=c(0.975))
df_fit_I = data.frame(median_I, low_I, high_I, times_pred)

fit_A <- posts_vb_1$fake[,,2]
fit_SIR_vb_A <- fit_A
median_A = apply(fit_SIR_vb_A, 2, median)
low_A = apply(fit_SIR_vb_A, 2, quantile, probs=c(0.025))
high_A = apply(fit_SIR_vb_A, 2, quantile, probs=c(0.975))
df_fit_A = data.frame(median_A, low_A, high_A, times_pred)
#save(df_fit_I_vb_1,file="df_I_det_Poiss_vb.Rda")

#df_sample_N = data.frame(hiv_data, sample_time)  

ggplot() +
  geom_ribbon(aes(x=times_pred, ymin = low_I, ymax = high_I), fill = "orange", alpha = 0.6) +
  geom_point(data = HIV_people, aes(x=sample_time, y=hiv_data) ,shape = 19, size = 1.5) +
  geom_line(data = df_fit_I, aes(x=times_pred, y=median_I, color = "Median"), size = 1.1) +
  scale_colour_manual(name='', values=c('Data'='black', 'Median'='darkorange3'))+
#  guides(colour = guide_legend(override.aes = list(shape=c(16,NA), linetype=c(0,1))))+
#  theme_bw()+theme(text = element_text(size=20))+
  
  geom_ribbon(aes(x=times_pred, ymin = low_A, ymax = high_A), fill = "light blue", alpha = 0.6) +
  geom_point(data = AIDS_people, aes(x=sample_time, y=aids_data) ,shape = 19, size = 1.5) +
  geom_line(data = df_fit_A, aes(x=times_pred, y=median_A, color = "Median"), size = 1.1) +
  scale_colour_manual(name='', values=c('Data'='red', 'Median'='darkorange3'))+
#  guides(colour = guide_legend(override.aes = list(shape=c(16,NA), linetype=c(0,1))))+
  labs(x = "Time (days)", y = "HIV-AIDS cases ") + 
  scale_x_continuous(limits=c(0, 30)) +
  scale_y_continuous(limits=c(0,8000)) +
  theme_bw()+theme(text = element_text(size=20))
  
 
```


```{r plot_advi_1, echo=FALSE}
# Model fitted values across the observed time period
#library(gridExtra)
fit_I <- posts_vb_1$fake[,,1]
fit_SIR_vb_I <- fit_I
median_I = apply(fit_SIR_vb_I, 2, median)
low_I = apply(fit_SIR_vb_I, 2, quantile, probs=c(0.025))
high_I = apply(fit_SIR_vb_I, 2, quantile, probs=c(0.975))
df_fit_I = data.frame(median_I, low_I, high_I, times_pred)

fit_A <- posts_vb_1$fake[,,2]
fit_SIR_vb_A <- fit_A
median_A = apply(fit_SIR_vb_A, 2, median)
low_A = apply(fit_SIR_vb_A, 2, quantile, probs=c(0.025))
high_A = apply(fit_SIR_vb_A, 2, quantile, probs=c(0.975))
df_fit_A = data.frame(median_A, low_A, high_A, times_pred)
#save(df_fit_I_vb_1,file="df_I_det_Poiss_vb.Rda")

#df_sample_N = data.frame(hiv_data, sample_time)

ggplot() +
   geom_point(data = HIV_people, aes(x=sample_time, y=hiv_data,color="black") ,shape = 19, size = 1.5) +
  geom_ribbon(aes(x=times_pred, ymin = low_I, ymax = high_I), fill = "orange", alpha = 0.6) +

  geom_line(data = df_fit_I, aes(x=times_pred, y=median_I, color = "Median"), size = 1.1) +
   
#  scale_colour_manual(name='', values=c('Data'='black', 'Median'='darkorange3'))+
#  guides(colour = guide_legend(override.aes = list(shape=c(16,NA), linetype=c(0,1))))+
#  theme_bw()+theme(text = element_text(size=20))+
  
  geom_ribbon(aes(x=times_pred, ymin = low_A, ymax = high_A), fill = "light blue", alpha = 0.6) +
  geom_point(data = AIDS_people, aes(x=sample_time, y=aids_data,color="black") ,shape = 19, size = 1.5) +
  geom_line(data = df_fit_A, aes(x=times_pred, y=median_A, color = "Median"), size = 1.1) +
  scale_colour_manual(name='', values=c('Data'='black', 'Median'='darkblue'))+
#  guides(colour = guide_legend(override.aes = list(shape=c(16,NA), linetype=c(0,1))))+
  labs(x = "Time (days)", y = "HIV-AIDS cases ") + 
  scale_x_continuous(limits=c(0, 26)) +
  scale_y_continuous(limits=c(0,8000)) +
  theme_bw()+theme(text = element_text(size=20))
  
 
```



```{r plot_advi_1, echo=FALSE}
# Model fitted values across the observed time period
fit_A <- posts_vb_1$y_hat[,,2]
fit_SIR_vb_A <- fit_A
median_A = apply(fit_SIR_vb_A, 2, median)
low_A = apply(fit_SIR_vb_A, 2, quantile, probs=c(0.025))
high_A = apply(fit_SIR_vb_A, 2, quantile, probs=c(0.975))
df_fit_A = data.frame(median_A, low_A, high_A, sample_time)
#save(df_fit_I_vb_1,file="df_I_det_Poiss_vb.Rda")

df_sample_N = data.frame(aids_data, sample_time)

ggplot(df_sample_N, aes(x=sample_time, y=aids_data)) +
  geom_ribbon(aes(x=sample_time, ymin = low_A, ymax = high_A), fill = "light green", alpha = 0.6) +
  geom_line(data = df_fit_A, aes(x=sample_time, y=median_A, color = "Median"), size = 1.3) +
  geom_point(shape = 19, size = 3, (aes(color="Data"))) +
  scale_colour_manual(name='', values=c('Data'='black', 'Median'='darkorange3'))+
  guides(colour = guide_legend(override.aes = list(shape=c(16,NA), linetype=c(0,1))))+
  labs(x = "Time (days)", y = "AIDS students") + 
  scale_x_continuous(limits=c(0, 35)) +
  scale_y_continuous(limits=c(0,100)) +
  theme_bw()+theme(text = element_text(size=20))
```




```{r plot_advi_1, echo=FALSE}
# Model fitted values across the observed time period
fit_I_vb_1 <- posts_vb_1$y_hat
fit_SIR_vb_1 <- fit_I_vb_1
median_I_vb_1 = apply(fit_SIR_vb_1, 2, median)
low_I_vb_1 = apply(fit_SIR_vb_1, 2, quantile, probs=c(0.025))
high_I_vb_1 = apply(fit_SIR_vb_1, 2, quantile, probs=c(0.975))
df_fit_I_vb_1 = data.frame(median_I_vb_1, low_I_vb_1, high_I_vb_1, sample_time)
#save(df_fit_I_vb_1,file="df_I_det_Poiss_vb.Rda")

df_sample_N = data.frame(hiv_data, sample_time)

ggplot(df_sample_N, aes(x=sample_time, y=hiv_data)) +
  geom_ribbon(aes(x=sample_time, ymin = low_I_vb_1, ymax = high_I_vb_1), fill = "light green", alpha = 0.6) +
  geom_line(data = df_fit_I_vb_1, aes(x=sample_time, y=median_I_vb_1, color = "Median"), size = 1.3) +
  geom_point(shape = 19, size = 3, (aes(color="Data"))) +
  scale_colour_manual(name='', values=c('Data'='black', 'Median'='darkorange3'))+
  guides(colour = guide_legend(override.aes = list(shape=c(16,NA), linetype=c(0,1))))+
  labs(x = "Time (days)", y = "Number of Infected students") + 
  scale_x_continuous(limits=c(0, 35)) +
  scale_y_continuous(limits=c(0,100)) +
  theme_bw()+theme(text = element_text(size=20))
```


The resulting 95$\%$ credible intervals from ADVI have shorter length compared to NUTS.
Also, adding stochasticity improves the fit to the data.


Summing up, the results of both the deterministic and the stochastic setting bring us to the preliminary conclusion that if we are interested in real-time inference both methods are feasible and efficient. In terms of computational time ADVI is extremely efficient.
